---
title: "Cumulative_Seasonal_Emissions"
author: "Zhang"
output:
  pdf_document:
    toc: yes
editor_options:
  markdown:
    wrap: sentence
---
# Necessary libraries

```{r message=FALSE,warning=FALSE}
library(knitr)
library(ggplot2)
theme_set(theme_bw())
library(emmeans)
library(multcomp)
library(PLS205)
library(lme4)
library(lmerTest)
library(multcompView)
library(car)
library(Rmisc) 
library(dplyr) #https://r4ds.had.co.nz/ (Chapter 3, Chapter 5, look at filter and select)
# https://bookdown.org/ansellbr/WEHI_tidyR_course_book/
library(stringr) 
library(data.table)
library(GGally)
library(formatR)
library(readxl)
library(openxlsx)
library(zoo)
library(dplyr)
library(tidyr)
library(zoo)


```

# Read Excel daily flux values from obtained from Li-Cor and GC methodologies

```{r}
licor <- read_excel("../Computed_Flux/all_fluxes_licor.xlsx", sheet = 1)
licor$Plot <- as.factor(licor$Plot)

GC <- read_excel("../Computed_Flux/GC_2025_CH4_N2O_Flux.xlsx", sheet = 1) %>%
            mutate(Treatment = factor(str_sub(Plot, 2)))

str(licor)
str(GC)

#flux %>%
#  summarise(n_dates = n_distinct(Date))
```

# Combine into one big dataframe

```{r}
N2O_2025 <- GC %>% 
            select(-CH4_flux_g_ha_day)  # thats all the N2O dates. Other than these, N2O is 0.

CH4_GC <- GC %>% select(-N2O_flux_g_ha_day) %>% drop_na()

CH4_2025 <- rbind(CH4_GC, licor)

# Join CH4_2025 with N2O_2025 by Plot and Date
flux_2025 <- CH4_2025 %>%
  left_join(N2O_2025 %>% select(Plot, Date, N2O_flux_g_ha_day),
            by = c("Plot", "Date")) %>%
  # Replace NA in N2O_flux_g_ha_day with 0
  mutate(N2O_flux_g_ha_day = if_else(is.na(N2O_flux_g_ha_day), 0, N2O_flux_g_ha_day)) #during continuous flooded conditions, there are is no N2O emissions

write.xlsx(flux_2025, file= "../Computed_Flux/Final_Flux_2025_CH4_N2O.xlsx", sheetName = "1", rowNames = FALSE)
```

# Linear interpolation and cumulative seasonal (CH4 and N2O)

```{r}
flux_2025 <- flux_2025 %>%
  filter(Date >= as.POSIXct("2025-05-10") & Date <= as.POSIXct("2025-10-06"))

start_date <- as.Date("2025-05-16")
end_date <- as.Date("2025-09-24")
date_seq <- seq.Date(start_date, end_date, by = "day")

flux_2025_rice_interpolated <- flux_2025 %>%
  group_by(Plot) %>%
  complete(Date = date_seq) %>%
  ungroup()

flux_2025_rice_interpolated <- flux_2025_rice_interpolated %>%
  group_by(Plot) %>%
  mutate(CH4_flux_g_ha_day = na.approx(CH4_flux_g_ha_day, rule = 2)) %>%
  mutate(N2O_flux_g_ha_day = na.approx(N2O_flux_g_ha_day, rule = 2)) %>%
  ungroup()

flux_2025_rice_seasonal_emissions <- flux_2025_rice_interpolated %>%
  group_by(Plot) %>%
  summarize(total_CH4_emissions = sum(CH4_flux_g_ha_day, na.rm = TRUE),
            total_N2O_emissions = sum(N2O_flux_g_ha_day, na.rm = TRUE)) %>%
  mutate(Period_Year = "Summer_2025") %>%
  mutate(Period = "Summer") %>%
  mutate(total_CH4_emissions_kg_ha = total_CH4_emissions/1000) %>%
  mutate(total_N2O_emissions_kg_ha = total_N2O_emissions/1000) %>%
  mutate(GWP = total_CH4_emissions_kg_ha*28+total_N2O_emissions_kg_ha*265) %>% #compute GWP using CH4 (28) and N2O (265) %>%
  mutate(Treatment = factor(str_sub(Plot, 2)))

ggplot(flux_2025_rice_interpolated, aes(y=CH4_flux_g_ha_day, x=Date, color = Plot)) + geom_point()
ggplot(flux_2025_rice_interpolated, aes(y=N2O_flux_g_ha_day, x=Date, color = Plot)) + geom_point()
```

# CH4 over time 

```{r}
CH4_flux_graphing <- flux_2025 %>%
  group_by(Treatment, Date) %>%
  mutate(CH4_flux_g_ha_day_se = sd(CH4_flux_g_ha_day)/sqrt(5)) %>%
  summarise(CH4_flux_g_ha_day = mean(CH4_flux_g_ha_day),
  CH4_flux_g_ha_day_se = mean(CH4_flux_g_ha_day_se))


CH4_over_time <- ggplot(CH4_flux_graphing, aes(x = Date, y = CH4_flux_g_ha_day,  colour =  Treatment))+
  geom_point()+
  geom_line()+
  labs(y = expression("Daily CH"[4]~"Flux (g ha"^-1~" day"^-1~")")) +
  geom_errorbar(aes(ymin=CH4_flux_g_ha_day-CH4_flux_g_ha_day_se, ymax=CH4_flux_g_ha_day+CH4_flux_g_ha_day_se), size=0.5)

CH4_over_time

ggsave(CH4_over_time, filename = "../Figures/CH4_over_time.jpg", height = 25, width = 25, units = "cm", dpi=400)
```


# N2O over time 

```{r}
N2O_flux_graphing <- flux_2025 %>%
  group_by(Treatment, Date) %>%
  mutate(N2O_flux_g_ha_day_se = sd(N2O_flux_g_ha_day)/sqrt(5)) %>%
  summarise(N2O_flux_g_ha_day = mean(N2O_flux_g_ha_day),
  N2O_flux_g_ha_day_se = mean(N2O_flux_g_ha_day_se))


N2O_over_time <- ggplot(N2O_flux_graphing, aes(x = Date, y = N2O_flux_g_ha_day,  colour =  Treatment))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=N2O_flux_g_ha_day-N2O_flux_g_ha_day_se, ymax=N2O_flux_g_ha_day+N2O_flux_g_ha_day_se), size=0.5)

N2O_over_time

ggsave(N2O_over_time, filename = "../Figures/N2O_over_time.jpg", height = 25, width = 25, units = "cm", dpi=400)
```

# CH4 stats

```{r}
CH4_model <- lm(total_CH4_emissions_kg_ha~Treatment, data=flux_2025_rice_seasonal_emissions)
anova(CH4_model)

CH4_means = emmeans(CH4_model,spec = 'Treatment')
CH4_effects = contrast(CH4_means, method = 'pairwise', adjust = "Tukey")
summary(CH4_effects)

cld(CH4_means)
```

# N2O stats

```{r}
N2O_model <- lm(total_N2O_emissions_kg_ha~Treatment, data=flux_2025_rice_seasonal_emissions)
anova(N2O_model)

N2O_means = emmeans(N2O_model,spec = 'Treatment')
N2O_effects = contrast(N2O_means, method = 'pairwise', adjust = "Tukey")
summary(N2O_effects)

cld(N2O_means)
```


# GWP stats

```{r}
GWP_model <- lm(GWP~Treatment, data=flux_2025_rice_seasonal_emissions)
anova(GWP_model)

GWP_means = emmeans(GWP_model,spec = 'Treatment')
GWP_effects = contrast(GWP_means, method = 'pairwise', adjust = "Tukey")
summary(GWP_effects)

cld(GWP_means)
```


# Linear interpolation demo 


linear_interpolation_demo <- flux %>% filter(Plot == "A50")

ggplot(linear_interpolation_demo, aes(y=CH4_flux_g_ha_day, x=Date, color = Plot)) + geom_point()

ggplot(linear_interpolation_demo, aes(y=CH4_flux_g_ha_day, x=Date, color = Plot)) + geom_point() +geom_line()

ggplot(flux_2025_rice_interpolated%>%filter(Plot=="A50"), aes(y=CH4_flux_g_ha_day, x=Date, color = Plot)) + geom_point()

ggplot(flux_2025_rice_interpolated %>% filter(Plot == "A50"),
       aes(x = Date, y = CH4_flux_g_ha_day, color = Plot)) +
  geom_point() +
  geom_col(alpha = 0.5, fill = "red")


