---
title: "GC_Flux "
author: "Zhang Zhenglin"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float: yes
editor_options:
  markdown:
    wrap: sentence
---
# Necessary libraries

```{r message=FALSE,warning=FALSE}
library(knitr)
library(ggplot2)
theme_set(theme_bw())
library(emmeans)
library(multcomp)
library(PLS205)
library(lme4)
library(lmerTest)
library(multcompView)
library(car)
library(Rmisc) 
library(dplyr) #https://r4ds.had.co.nz/ (Chapter 3, Chapter 5, look at filter and select)
# https://bookdown.org/ansellbr/WEHI_tidyR_course_book/
library(stringr) 
library(data.table)
library(GGally)
library(formatR)
library(readxl)
library(FluxCalR)
library(tidyverse)
library(fuzzyjoin)
library(purrr)
library(data.table)
library(broom)
library(lubridate)
library(readxl)
library(openxlsx)
library(ggrepel)
library(Peak2Flux2)
```

# Load excel files

The Standard calibration file (Std_Input.csv) and the sample file (Input_samples_No_ppm.csv) on GitHub are located in the directory: XiaoZhangZhangRice/Peak2Flux2/data

```{r}
#Read Standard Calibration File
std <- read.csv("../Field_Data/GC_Data/Std_Input.csv")

#Read Sample File
samples <- read_excel("../Field_Data/GC_Data/Input_samples_No_ppm.xlsx")
```

# Peak to PPM

This function uses data entries in the standard calibration file to create calibration curves for each individual GC run using peak areas and gas standard ppms. Afterwards, the concentration of samples (ppm) are generated from the peak areas in the samples file and the calibration curves constructed from the standard file. 

```{r}
sample_ppm <- peak2ppm(std, samples)

sample_ppm
```

# PPM to flux


```{r}
Final_data <- ppm2flux(sample_ppm, CH4_mass = 16, N2O_mass = 44, Timesteps = 4, Diagnostics = FALSE)

Final_data$CH4_flux_g_ha_day <- Final_data$CH4_flux_corrected*24*0.001*10000
Final_data$N2O_flux_g_ha_day <- Final_data$N2O_flux_corrected*24*0.001*10000


str(Final_data)

GC_Fluxes <- Final_data %>% select(Plot, Date, CH4_flux_g_ha_day, N2O_flux_g_ha_day)

write.xlsx(GC_Fluxes, file= "../Field_Data/GC_Data/GC_Fluxes.xlsx", sheetName = "1", rowNames = FALSE)

```
